Analysis of Cartesian Genetic Programming's Evolutionary Mechanisms

### 2014-03-26 CGP Journal/main.tex
Finally down to 15 pages again!

As both output locations and information flow in the DAG are evolvable, often
only a tiny fraction of the genome participates in creating the
output values.  These nodes are referred to as ``active,'' with the nodes not
being used to create output values referred to as ``inactive.''  Inactive nodes
allow CGP individuals to drift genetically, as they can be mutated without effecting
the fitness of the individual.  This genetic drift can then be incorporated, as
mutation can change the DAG structure causing previously inactive nodes to become
active.  Previous work suggests CGP is most efficient when up to 95\% of the genome
is inactive~\cite{miller:2006:redundancy}, while more recent work suggests this may
be a result of hidden parsimony pressure in CGP~\cite{goldman:2013:ordering}.

>>>>

As both output locations and information flow in the DAG are evolvable, often
only a tiny fraction of the genome participates in creating the
output values.  These nodes are referred to as ``active,'' with the nodes not
being used to create output values referred to as ``inactive.''  Inactive nodes
%TODO Changed here
allow for genetic drift, as individuals can be mutated without effecting
their fitness.  These mutations can then be incorporated, as future
mutations can change the DAG structure causing previously inactive nodes to become
active.  Previous work suggests CGP is most efficient when up to 95\% of the genome
is inactive~\cite{miller:2006:redundancy}, while more recent work suggests this may
be a result of hidden parsimony pressure in CGP~\cite{goldman:2013:ordering}.
